---
title: "LLCU255 Data and Literary study"
subtitle: "Individual Assignment 2"
author: "Shenshun Yao 260709204"
date: "15/09/2020"
abstract: "In this assignment, our goal is to get comfortable working with tables in R based on Novel150 data set."
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
```
First,  we set working directory, load table and print the name of each column.

```{r}
setwd("~/Desktop/Fall_2020/LLCU255_IntrotoTextMining/Individual Assignment 2")
a<-read.csv("txtlab_Novel150_English.csv")
colnames(a)
```
## Problem 1
How many documents are there? How many variables? 

### Solution:
```{r}
# To get the number of documents, count the number of rows using nrow()
nrow(a)
```
There are 150 documents(rows) in total, each document has 9 features(columns), so we have 1350 variables.

## Problem 2
How many arthurs are there?

### Solution:
```{r}
# unique() returns a vector, data frame or array with duplicate elements/rows remove
length(unique(a$author) )
```
There are 98 authors.

## Problem 3
Name a novel other than one by Jane Austen that you've read in this data.

### Solution:
```{r}
# Create a subset of Novel150 data set without the novels written by Jane Austen
a_1<-subset(a, a$author!="Austen,Jane")
# Select a random element in the column"title"
sample(a_1$title, 1)
```
A random selected answer was printed.

## Problem 4
What is the ratio of first-person to third person novels in our sample?

### Solution:
```{r}
# Count the number of first-person and third-person novels respectively.
numberofFirstperson<-length(a$person[a$person == "first"])
numberofThirdperson<-length(a$person[a$person == "third"])
# Then divide them to get the ratio
ratio<-numberofFirstperson/numberofThirdperson
ratio
```
The ratio is 0.4018692.

## Problem 5
What is the avg length of first and third person novels? Does the difference seem large to you?

### Solution:
```{r}
# firstperson<-subset(a, a$person == "first")
# firstperson_avg<-mean(firstperson$length)
# firstperson_avg
# thirdperson<-subset(a, a$person == "third")
# thirdperson_avg<-mean(thirdperson$length)
# thirdperson_avg
# A faster way to do these calculations
tapply(a$length, a$person, mean)
```
I think the difference does not seam large to me.

## Problem 6
What is the average length of 1P novels by women? How does this compare to 3P novels by women?

### Solution:
```{r}
female<-a[a$gender == "female",]
tapply(female$length, female$person, mean)
```
The average length of 1P novels by women is 102254.5 which is less than 3P novels by women(133519.6).

## Problem 7
List the avg. length of novels by decade. What do you observe? Figure out how to plot for extra credit (insert screen shot here).

### Solution:
```{r}
# Convert the date column to a column of strings to utilize the substring function
a$decade<-as.character(a$date)
# Transform the 4th digit to a 0
substring(a$decade, 4, 4) <- "0"
# Convert back to integers
a$decade<-as.numeric(a$decade)
# Treat decades as factors in order to see what the avg. length is by decade.
dec.length<-tapply(a$length, as.factor(a$decade), mean)
dec.length
```

Already listed the avg. length of novels by decade. I observed that the avg.length of novels by decade was fluctuate and reached the peak in 1860. I used ggplot the visualized the result.

```{r out.width = "60%", fig.align= 'center'}
#scatterplot
dec.length.df<-as.data.frame(dec.length)
ggplot(aes(x = row.names(dec.length.df), y = dec.length), data = dec.length.df)+
  geom_point()+
  labs(x="Decade", y="Average Length")
```

Another way to visualize this is through the use of boxplots. These allow you to see the range of values for each decade which will give you a better sense of those periods that are particularly different.

```{r out.width = "60%", fig.align='center'}
ggplot(a, aes(x=factor(decade), y=length)) + 
  geom_boxplot()+
  labs(x="Decade", y="Length")
```