---
title: "LLCU255 Assignment2"
author: "Shenshun Yao 260709204"
date: "15/09/2020"
abstract: "In this assignment, our goal is to get comfortable working with tables in R based on Novel150 data set."
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
```
First,  we set working directory, load table and print the name of each column.

```{r}
setwd("~/Desktop/Fall_2020/LLCU255_IntrotoTextMining/Individual Assignment 2")
a<-read.csv("txtlab_Novel150_English.csv")
colnames(a)
```
## Problem 1
How many documents are there? How many variables? 

### Solution:
```{r}
# To get the number of documents, count the number of rows using nrow()
nrow(a)
```
There are 150 documents(rows) in total, each document has 9 features(columns), so we have 1350 variables.

## Problem 2
How many arthurs are there?

### Solution:
```{r}
# unique() returns a vector, data frame or array with duplicate elements/rows remove
length(unique(a$author) )
```
There are 98 authors.

## Problem 3
Name a novel other than one by Jane Austen that you've read in this data.

### Solution:
```{r}
# Create a subset of Novel150 data set without the novels written by Jane Austen
a_1<-subset(a, a$author!="Austen,Jane")
# Select a random element in the column"title"
sample(a_1$title, 1)
```
A random selected answer was printed.

## Problem 4
What is the ratio of first-person to third person novels in our sample?

### Solution
```{r}
# Count the number of first-person and third-person novels respectively.
numberofFirstperson<-length(a$person[a$person == "first"])
numberofThirdperson<-length(a$person[a$person == "third"])
# Then divide them to get the ratio
ratio<-numberofFirstperson/numberofThirdperson
ratio
```
The ratio is 0.4018692.

## Problem 5
What is the avg length of first and third person novels? Does the difference seem large to you?

```{r}
firstperson<-subset(a, a$person == "first")
firstperson_avg<-mean(firstperson$length)
firstperson_avg
thirdperson<-subset(a, a$person == "third")
thirdperson_avg<-mean(thirdperson$length)
thirdperson_avg
```
I think the difference does not seam large to me.

